Stock forecasting methods and their usage

### 2015-06-01 Paper_self.tex
added description of second algorithm

We implemented three different algorithms to predict stock prices and maximise the outcome. All three of them only consider one stock at a time. In this section we will describe the algorithms we used

@@

TODO: algorithmus beschreiben mit dem neuesten Trend der beispielweiße die nächsten 5 tage vorraussagen kann.

>>>>

We implemented three different algorithms to predict stock prices and maximise the outcome. All three of them only consider one stock at a time and do not take any global news or trends in account. In this section we will describe the algorithms we used in detail

@@

With this algorithm we wanted to make a precise prediction on the stock market. It analyses the closing prices of a specific stock and gives a forecast how the price will develop. We also wanted the algorithm to be able to predict not only the price for the next day, but for the next few days. In section \ref{results} we will demonstrate that we were able to do a good prediction even 4 days in the future. But it must be said that the more in the future the prediction is, the bigger the gap between the real prices and the prediction.
\\
The algorithm itself uses only the last few days of a stock. The number of days used for this algorithm is not static. The amount of days that give the best result may vary for different stocks. Nevertheless if the number of days stays within a specific range, the results are pretty accurate.
\\
\\
\[ M = \sum_{n=0}^D C_{n+1} - C_{n} \]
\[ prediction = \frac{M}{D}\]
\[ stock_{predicted} = stock_{today} + prediction\]
\\
With D the number of days the prediction is based on and C the closing price of the nth day. After you calculated the prediction, the only thing that is left to do, is adding the prediction to the actual stock price. The predicted stock price here is for the next day only. 
\\
To get the prediction for the day after that, do this calculation again but take the predicted stock into account.It is possible to do this over and over again for as many days in the future as you would like. Though it is not meaningful for more than a few days because the prediction gets more and more unreliable. For detailed results an the amount of days that are rational, see chapter \ref{results} on page \pageref{results}.
